Biotic invasions fuck with the manageability of pollination networks

### 2017-02-21 paper/supp_info_2.Rmd
Fix the reading of the new all matchings

```{r table-correlations-visitation-vs-efficiency, echo = FALSE, warning = F, message = F, results = "asis"}
d_sp <- driver %>%
  plyr::ldply(function(x) {
    get_frequencies(x) %>%
      dplyr::mutate(type = attr(x, "type"),
                    scaled = attr(x, "scaled"))
  }) %>%
  dplyr::inner_join(meta)

>>>>

```{r table-correlations-visitation-vs-efficiency, echo = FALSE, warning = F, message = F, results = "asis"}
d_sp <- driver %>%
  plyr::ldply(function(x) {
    o <- get_frequencies(x) %>%
      dplyr::mutate(type = attr(x, "type"),
                    scaled = attr(x, "scaled"))
    net_names_with_extension <- unique(o$net_name) %>% as.character()
    net_names_without_extension <- 
    	strsplit(net_names_with_extension, "_", fixed = T) %>%
    	lapply(function(x){ 
    		if(x[length(x)] %in% LETTERS) {
    			x[-length(x)]
    		} else {
    			x
    		}
    		}) %>%
    	lapply(paste, collapse = "_") %>% unlist()
    o %>% dplyr::mutate(
    	net_name = plyr::mapvalues(net_name, net_names_with_extension,
    														 net_names_without_extension)
    )
  }) %>%
  dplyr::inner_join(meta)
